Data Cleaning

### 2025-12-05 Data Cleaning.Rmd
Re-made the joining of dosign and rwar datasets after merge issues.

write_csv(merged_daily_data, )
```

>>>>

#write_csv(merged_daily_data, )
```

```{r}
# Merge dosing data to this data. Have significant overlap
dosing <- read.csv("CoagulantDoses_2017-20.csv") |>
  rename(Timestamp = Date) |> 
  mutate(Timestamp = mdy(dosing$Timestamp))

RWAR_dosing_cleaned <- inner_join(dosing, merged_daily_data)
summary(RWAR_dosing_cleaned) #can export to csv with same name

```{r}
water_lm <- lm(Ferric.chloride..mg.L ~ ., 
               data=RWAR_dosing_cleaned |> select(-c(Timestamp, Cationic.Polimer..mg.L)))
summary(water_lm)

```{r}
data <- read.csv("RWAR_dosing_cleaned.csv")
lagged_data <- data |>
  mutate(Temp_lag1 = lag(mean_Temp, 1), 
         Temp_lag2 = lag(mean_Temp, 2),
         pH_lag1 = lag(mean_pH, 1),
         pH_lag2 = lag(mean_pH, 2),
         Cond_lag1 = lag(mean_Conductivity, 1),
         Cond_lag2 = lag(mean_Conductivity, 2),
         Turb_lag1 = lag(mean_Turbidity, 1),
         Turb_lag2 = lag(mean_Turbidity, 2))
# Temp
lagged_data$Temp_lag1[1] <- lagged_data$Temp_lag1[2]
lagged_data$Temp_lag2[1:2] <- lagged_data$Temp_lag2[3]
# pH
lagged_data$pH_lag1[1] <- lagged_data$pH_lag1[2]
lagged_data$pH_lag2[1:2] <- lagged_data$pH_lag2[3]
# Conductivity
lagged_data$Cond_lag1[1] <- lagged_data$Cond_lag1[2]
lagged_data$Cond_lag2[1:2] <- lagged_data$Cond_lag2[3]
# Turbidity
lagged_data$Turb_lag1[1] <- lagged_data$Turb_lag1[2]
lagged_data$Turb_lag2[1:2] <- lagged_data$Turb_lag2[3]

lm_fit <- lm(Ferric.chloride..mg.L ~ ., data=lagged_data |> select(-c(Timestamp)))
summary(lm_fit)
